Adaptive Resolution Simulation: Theoretical Fundations and Open Questions

### 2014-10-17 writeDown/pub.epj/paper.tex
add results of dynamical properties of alanine system

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fw}}
\newcommand{\bwd}[0]{\textrm{bw}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mh}[0]{\mathcal {H}}
\newcommand{\dist}[0]{\textrm {dist}}
\newcommand{\AT}[0]{\textrm{AT}}
\newcommand{\HY}[0]{\textrm{HY}}
\newcommand{\CG}[0]{\textrm{CG}}
\newcommand{\EX}[0]{\textrm{EX}}
\newcommand{\moleidxone}[0]{i}
\newcommand{\moleidxtwo}[0]{j}
\newcommand{\atomidxone}[0]{\alpha}
\newcommand{\atomidxtwo}[0]{\beta}
\newcommand{\thf}{{\textrm{th}}}
\newcommand{\rdf}{{\textrm{rdf}}}
\newcommand{\rep}{{\textrm{rep}}}
\newcommand{\dof}{{\textrm{DOF}}}
\newcommand{\exc}{{\textrm{extra}}}
\newcommand{\inv}{{\textrm{equi}}}

@@

Both the atomistic and coarse-grained intermolecular interactions are
well defined in the atomistic region and coarse-grained regions,
respectively.  To setup an AdResS simulation, one needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (saying $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$, from the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

The potential interpolation approach defines the hybrid energy by the same idea:
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscipt ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
It should be noted that
the last term breaks the Newton's third law, therefore the force of potential interpolation
does not conserves the momentum.

@@

@@

To consider the accuracy of the AdResS simulation, we always compare it with a
atomistic reference system, which is of the same size as the AdResS system, and contains the same number of molecules.
If the statistal properties of the atomistic region in the AdResS simulation
is same as the corresponding subregion in the atomistic reference, then
the atomistic region is embeded into the AdResS system as if it were embeded in to
an atomistic environment, and the AdResS simulation is of good accuracy.

@@

\subsection{The accuracy of the configurational probability density}
The configurational probability density~\ref{eqn:dist-1-0} is further splitted as
\begin{align}
  p(\vect x_\AT \vert N_\AT) =
  \sum_{N_\HY} \int {d}\vect x_\HY\,
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)\cdot
  p(\vect x_\HY, N_\HY\vert N_\AT)  
\end{align}
The first probability density in the integral is the probability density
of atomistic DOFs conditioned on the number of atomistic molecules and all
hybrid DOFs.
It can shown that if
(1) all interactions in the system are cut-offed;
(2) The atomistic region interacts with the bybrid region only in an atomistic way;
(3) The system is short-range correlated, and the correlation between the atomistic
and the coarse-grained regions is negligible, then the probability density $p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)$
is approximated by
\begin{align}\label{eqn:dist-conf-0}
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)
  \propto
  \exp\Big\{-\beta \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY) \Big\},
\end{align}
where 
\begin{align}
  \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY)
  =
  \sum_{i=1}^{N_\AT}\frac12 m_i\vect v_i^2 +
  \sum_{i,j=1}^{N_\AT} \frac12 V^\AT(\vect r_{ij}) +
  \sum_{i=1}^{N_\AT}\sum_{j=N_\AT+1}^{N_\AT + N_\HY} V^\AT(\vect r_{ij})
\end{align}
is the atomistic Hamiltonian with parameters $\vect x_\HY, N_\HY$. It
should be noted that the probability density~\eqref{eqn:dist-conf-0}
is identical to that of the reference system with a subregion that
corresponds to the hybrid region.
The probability density and local Hamiltonian
can be written down for the coarse-grained region analogically.

@@

For the 
In Ref.~\cite{wang2013grand}, it has been shown that

\section{Dynamical properties: adaptive resolution simulation beyond equilibrium}
citation~\cite{wang2014exploring}

>>>>

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fw}}
\newcommand{\bwd}[0]{\textrm{bw}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mh}[0]{\mathcal {H}}
\newcommand{\dist}[0]{\textrm {dist}}
\newcommand{\AT}[0]{\textrm{AT}}
\newcommand{\HY}[0]{\textrm{HY}}
\newcommand{\CG}[0]{\textrm{CG}}
\newcommand{\EX}[0]{\textrm{EX}}
\newcommand{\moleidxone}[0]{i}
\newcommand{\moleidxtwo}[0]{j}
\newcommand{\atomidxone}[0]{\alpha}
\newcommand{\atomidxtwo}[0]{\beta}
\newcommand{\thf}{{\textrm{th}}}
\newcommand{\rdf}{{\textrm{rdf}}}
\newcommand{\rep}{{\textrm{rep}}}
\newcommand{\dof}{{\textrm{DOF}}}
\newcommand{\exc}{{\textrm{extra}}}
\newcommand{\equi}{{\textrm{eq}}}

@@

Both the atomistic and coarse-grained intermolecular interactions are
well defined in the atomistic region and coarse-grained regions,
respectively.  To setup an AdResS simulation, one needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (saying $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential,
unless the coarse-grained interaction is identical to the atomistic interaction~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$, from the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

The potential interpolation approach defines the hybrid energy by the same idea:
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscipt ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
This force is defined as the force of changing representation:
It should be noted that
the last term breaks the Newton's third law, therefore the force of potential interpolation
does not conserves the momentum.
We define the accumulative effect of this term by the force of changing representation:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

@@

\recheck{Remark, add the remark of inversed weighting function}

@@

To consider the accuracy of the AdResS simulation, we always compare it with a
atomistic reference system, which is of the same size as the AdResS system, and contains the same number of molecules.
If the statistal properties of the atomistic region in the AdResS simulation
is same as the corresponding subregion in the atomistic reference, then
the atomistic region is embeded into the AdResS system as if it were embeded in to
an atomistic environment, and the AdResS simulation is of good accuracy.
\recheck{comments on the ``atomistic region'' of the reference system}

@@

\subsection{The accuracy of the configurational probability density}
The configurational probability density~\eqref{eqn:dist-1-0} is further splitted as
\begin{align}
  p(\vect x_\AT \vert N_\AT) =
  \sum_{N_\HY} \int {d}\vect x_\HY\,
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)\cdot
  p(\vect x_\HY, N_\HY\vert N_\AT)  
\end{align}
The first probability density in the integral is the probability density
of atomistic DOFs conditioned on the number of atomistic molecules and all
hybrid DOFs.
It can shown that if
(1) all interactions in the system are cut-offed;
(2) The atomistic region interacts with the bybrid region only in an atomistic way;
(3) The system is short-range correlated, and the correlation between the atomistic
and the coarse-grained regions is negligible, then the probability density $p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)$
is approximated by
\begin{align}\label{eqn:dist-conf-0}
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)
  \propto
  \exp\Big\{-\beta \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY) \Big\},
\end{align}
where 
\begin{align}
  \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY)
  =
  \sum_{i=1}^{N_\AT}\frac12 m_i\vect v_i^2 +
  \sum_{i,j=1}^{N_\AT} \frac12 V^\AT(\vect r_{ij}) +
  \sum_{i=1}^{N_\AT}\sum_{j=N_\AT+1}^{N_\AT + N_\HY} V^\AT(\vect r_{ij})
\end{align}
is the atomistic Hamiltonian with parameters $\vect x_\HY, N_\HY$. It
should be noted that the probability density~\eqref{eqn:dist-conf-0}
is identical to that of the reference system with a subregion that
corresponds to the hybrid region.
The probability density and local Hamiltonian
can be written down for the coarse-grained region analogically.

@@

In the reference system, if the equilibrium state is achieved, then
the temperature, pressure and chemical potential of the atomistic and
coarse-grained subregions match. In AdResS system, the global uniform
temperture distrubution in equilibrium is impoosed by the Langevin
thermostat.  However, extra term appear in the pressure or chemical
potential relation when the momentum or energy conservation is absent
(see Tab.~\ref{tab:conv-laws}), respectively.

The chemical potential balance can be investigated from the fact that
when the uniform density distribution is guaranteed by thermodynamic force in equilibrium, the chemical potential
difference between the resolutions is compensited by $\omega_0$, which
is the work per molecule from the filter when a molecule leaves the
coarse-grained region and enters the atomistic region (see
relation~\eqref{eqn:mu-eq}).  Now the question turns out to be what
contributes to the work $\omega_0$.  For the potential interpolation,
the work of the filter is nothing but the work of the thermodynamic
force plus the extra kinetic energy corresponding to the extra DOFs
when a molecule obtains higher resolution:
\begin{align}\label{eqn:mu0-v}
  \omega_0 = \omega^{\thf,V} + \omega^\dof,
\end{align}
where $ \omega^{\thf,V}$ denotes the work of the thermodynamic force
of potential interpolation.
This work is path independent if the thermodynamic force is defined as a function of the distance to the atomistic region, and applies along the gradient of the weighting function.
We always assume the thermodynamic force satisfies these conditions.
For the force interpolation, 
we denote the extra contribution due to the absence of the enregy conservation
by $\omega^\exc$, then
\begin{align}\label{eqn:mu0-f}
  \omega_0 = \omega^{\thf} + \omega^\exc + \omega^\dof,
\end{align}
where $\omega^{\thf}$ is the work of the thermodynamic force of force interpolation.
The magnitude of the extra term $\omega^\exc$ is unclear up to now,
however, it is easy to computewith the help of the pressure relations.

For the force interpolation, the pressure of different resolutions
is related by~\cite{fritsch2012adaptive}
\begin{align}\label{eqn:p-eq-f}
  p_\CG - p_\AT = \rho_0 \:\omega^{\thf},
\end{align}
in which the work of the thermodynamic force again plays an important
role.  For the potential interpolation, the pressure relation can be
investigated by an imaginary infiniesimal volume increment of the atomistic
region, and the same amount of volume decrement of the coarse-grained
region. Following this idea, Ref.~\cite{agarwal2014chemical} proves that in
equilibrium the pressure between the resolutions is related by
\begin{align}\label{eqn:p-eq-v}
  p_\CG - p_\AT = \rho_0 (\omega^{\thf,V} - \omega^\rep)  
\end{align}
where $\omega^\rep$ is the work done by the average force of change representation:
\begin{align}\label{eqn:work-rep}
  \omega^\rep = \int \langle \vect F^\rep(\vect r)\rangle_V\circ d\vect r
\end{align}
where ``$\circ$'' means that the integral should be understood as along the path.
Since the force of changing representation acts always along the gradient of the weighting
function, therefore, if the system is homogeneous in the hybrid region, then the integral
is path independent. The ensemble average  can be estimated by sampling.
The force of changing representation merges from the last term of potential
interpolation~\eqref{eqn:f-v-interpol}, and contributes to the
pressure relation~\eqref{eqn:p-eq-v} because it does not satisfies the Newton's third
law.

Using Eq.~\eqref{eqn:mu0-v} and \eqref{eqn:mu0-f} one has $\omega^{\thf,V} - \omega^\thf = \omega^\exc$,
while using \eqref{eqn:p-eq-f} and \eqref{eqn:p-eq-v} one has $\omega^{\thf,V} - \omega^\thf = \omega^\rep$.
Therefore, we have 
\begin{align}
  \omega^\exc = \omega^\rep
\end{align}
which gives a explicit expression for the extra energy contribution
due to the absence of energy conservation in the force
interpolation. It should be noted that the ensemble averge in the work
of changing representation~\eqref{eqn:work-rep} is defined for the
potential interpolation, however, the estimate of the term
$\omega^\rep$ does not depend on the ensemble, at least up to the
``first order approximation''~\cite{agarwal2014chemical}, because the
hybrid region of the potential and force interpolation have the same
density. In Ref.~\cite{wang2013grand} an even strong conclusion is shown numerically in the SPC/E water system: The
averge force of changing representation estimated from potential
interpolation is pointwisly identical to that estimated from the force
interpolation. The thermodynamic relation discoved in
force and potential interpolation AdResS schemes are summarized
in Tab.~\ref{tab:thermodynamic}.

\begin{table}
  \centering
  \caption{A summary of the thermodynamic relations satisfied in force and potential interpolation AdResS.}
  \label{tab:thermodynamic}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}lll}\hline\hline
    &         Force interp. AdResS     &       Potential interp. AdResS \\
    Temperature    &   {$T_\AT = T_\CG$}                                                & {$T_\AT = T_\CG$}                                        \\
    Pressure       &   {$p_\CG - p_\AT = \rho_0\, \omega^\thf$}                          & {$p_\CG - p_\AT = \rho_0(\omega^{\thf,V} - \omega^\rep)$} \\
    Chemical pot.  &   {$\mu_\CG - \mu_\AT = (\omega^\thf + \omega^\dof +\omega^\rep)$}   & {$\mu_\CG - \mu_\AT = \omega^{\thf,V}+ \omega^\dof$}      \\\hline\hline
  \end{tabular*}
\end{table}

\section{Dynamical properties: adaptive resolution simulation beyond equilibrium}

\recheck{the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
}

\subsection{Velocity auto-correlation of water}

\subsection{Alanine dipeptide dissolved in water: equilibrium and dynamical properties}

\begin{figure}
  \centering
  \includegraphics[width=0.99\textwidth]{figs/system.alanine/all.eps}
  \caption{(a): A schematic plot of the alanine dipeptide molecule,
    and the two dihedral angles $\phi$ and $\psi$ that are used to
    represent the conformations of the molecule. (b) and (c): The free
    energy landscape plotted using variables $\phi$ and $\psi$.  (b)
    is for full atomistic reference simulation, while (c) is for
    AdResS simulation.}
  \label{fig:ala}
\end{figure}

The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
used as a testing case for computational method in simulating real
biomolecular system.
The system presents a very clear time-scale seperation: There are fast
motions like bond and angle vibration that happens on the time-scale of tens of femtoseconds, while
there are slow conformational changes that happens on the time-scale of hundreds of picoseconds.
The dihedral angles $\phi$ and $\psi$ (see
Fig.~\ref{fig:ala}~(a)) are usually chosen as slow variables that  describles
the molecular conformation and its transitions of the moelcules, which are of
general biological interest.

The free energy defined as the logrithm of equilibrium probability density over
$\phi$--$\psi$ space:
\begin{align}
  F(\phi,\psi) = -k_BT \ln p_\equi(\phi,\psi)
\end{align}
is plotted in Fig.~\ref{fig:ala}~(b) and (c). The AdResS free energy is
in good consistency with the full atomistic reference system. This is expected
at least in equilibrium, because as discussed in Sec.~\ref{sec:statistical}, the
AdResS sampling approximates the atomistic grand-canonical ensemble.

In pratice, not only the equilibrium probability density if of interest,
sometimes how the system relax to equilibrium is also of interest.
A direct analysis of the MD trajectories for these properties is not easy.
% Or equivalently
% at which timescale the slow dynamics  happens and from which conformation to which it corresponds to.
One possible solution is the Markov state model (MSM), which
approximate the original high-dimensional dynamics by a finite-state
Markov process (also called reduced dynamics),
and the original time-dependent probability density define on the phase
space $p_t(\vect x)$ is approximated by a  temporal discrete $\vect p_{k\tau}$ probability defined on the finite-state space.
The step of the temporal discretization $\tau$ is called the lag-time.
We always assume the reduced
dynamics is Markovian, although uaually it is not so in practice, and may become one of the main sources of the error.
It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
Due to the Markovianity of the reduced dynamics, the
probability at time $k\tau$ is given by
\begin{align}
\vect p_{k\tau} = \mathcal Q^k(\tau)\circ \vect p_0,
\end{align}
where $\mathcal Q(\tau)$ is the transfer operator
associated to the reduced dynamics. In equilibrium, the transfer operator is time-homogeneous.
Due to the Markovianity, for any $k$, we have
$p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t (\vect x)$.
If the propagator is irreducible and aperiodic, than according to Perron-Frobenius theorem, the maximum
eigenvalue is single and equal to 1.
If the dynamics
is further assumed to be reversible, then all eigenvalues of the propagator are
real valued.
The first $m$ largest eigenvalues are denoted by $1 = \lambda_1 > \lambda_2 \geq \lambda_3 \geq \cdots \geq \lambda_m$, and
the corresponding eigenvetors are denoted by $\Phi_1, \Phi_2, \cdots, \Phi_m$. The leading eigenvector is nothing but the
equilibrium probability that satisfies $\Phi_1 = \mathcal Q(\tau)\circ \Phi_1$.
The time evolution of the reduced probability density can be expaned by 
\begin{align}\label{eqn:expan}
  \vect p_{k\tau} = \Phi_1 + \sum_{i=2}^m e^{-\frac{k\tau}{t_i}} \,a_i\Phi_i + \textrm{fast decaying dynamics},
\end{align}
where $t_i$ is the timescale that corresponds to the $i$th eigenvalue:
\begin{align}\label{eqn:time-scale}
  t_i  = -\frac{\tau}{\log\lambda_i}, \quad i=2, \cdots, m,
\end{align}
and $a_i$ are constant that are determined by the initial state. As can be seen from Eq.~\eqref{eqn:expan}, the
time-dependent probability  converges to the equilibrium probability as time goes to infinity.
The timescale of the slow part of the relaxation is govenerned by the leanding eigenvectors through Eq.~\eqref{eqn:time-scale},
while the conformational change corresponds to each timescale is indicated by the eigenvector.
We assume a gap in the spectrum between $\lambda_m$ and the rest of the spectrum $\lambda_{m+1}, \cdots$,
therefore, the dynamics of the rest of the spectrum decays out very fast, and is not of particular interest.

The accuracy analysis of the MSM can be find in literature e.g.~\cite{}.

% The spectral anaysis of the MSM will reveal the
% implied timescales, and corresponding conformational changes.
% It has
% been proved that MSM is a good approximation to the original dynamics.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figs/system.alanine/fig-eig-val.png}
  \caption{The non-trivial leading timescale calculated from the
    Markov state modeling for the system of alanine dipeptide
    dissolved in water. In this figure, $t_2$ $t_3$ and $t_4$
    correspond to the first, second and third non-trivial leading
    timescale, respectively. The horizontal axis $\tau$ is the
    lag-time used to build the Markov state model. For a sufficient
    large $\tau$ the values of the timescales should be independent on
    the lag-time. The shadowing regions around the lines indicate the
    statistical uncertainty of the result. }
  \label{fig:ala-msm-t}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-2.eps}
  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-3.eps}
  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-4.eps}\\
  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-2.eps}
  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-3.eps}
  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-4.eps}\\
  \caption{The eigenvectors corresponding to the first three leading timescales.
    The first row presents the eigenvectors of the full atomistic reference, while the second
    row presents those of the AdResS simulation. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
    timescales $t_2$, $t_3$ and $t_4$ are given (see also Fig.~\ref{fig:ala-msm-t}). The magnitude of the eigenvectors are
    denoted by the color. 
    The conformational
    changes indicated by the eigenvectors are noted on the plots.}
  \label{fig:ala-msm-v}
\end{figure}

Here we present the eigenvalues and eigenvectors in
Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}, respectively. The
eigenvalue should be $\tau$ independent if the MSM is of good
accuracy. From the Fig.~\ref{fig:ala-msm-t}, the full atomistic
reference and the AdResS result are consistent within the statistical
uncertainty.  The eigenvectors of the AdResS are also consistent with
those of the full atomistic reference. Although calculated from the
equilibrium MD simulations, the leading timescales and the
corresponding eigenvectors are not the equilibrium properties, because
the transition probability (or the propagator) are actually
time-correlation functions, which are called dynamical properties in
this context. A good reproduction of the equilibrium properties does
not necessary implies a reproduction of the dynamical properties.
Although currently there is still no theoretical answer why AdResS is
so good in reproducing the dynamical properties, the provided
numercial example suggests that AdResS is promising in the applications
beyond equilibrium.
